Local real space operators for translating Stokes Q/U to E/B maps on the sphere

### 2017-10-16 article/sections/appendix.tex
Updates to the real space derivation sections of the paper

The spin spherical harmonic functions satisfy the following completeness relation,
%
\beq
\sum_{\ell m}{_sY_{\ell m}}(\hat{n}_i){_sY^*_{\ell m}}(\hat{n}_j) = \delta(\hat{n}_i - \hat{n}_j) \label{eq:ylmortho2} \,,
\eeq
%
Note that the numerical validity of \eq{eq:ylmortho2} is strictly true only when the sums over the indices $(\ell, m)$ run to infinity. This is never true in practice, since the measured data invariable are band limited owing to the finite resolution of the experiments. Hence this relation is only approximately true and in more realistic scenario takes up the following function form,
%
\beqry
\sum_{\ell=\ell_{\rm min}, m}^{\ell_{\rm max}}{_sY_{\ell m}}(\hat{n}_i){_sY^*_{\ell m}}(\hat{n}_j) &\approx& \delta(\hat{n}_i - \hat{n}_j) \label{eq:ylmortho2} \,, \\
&=& \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2 \ell+1}{4 \pi}} {}_{s}Y^{-s}_{\ell}(\beta,\alpha) e^{-i s \gamma} \,, \nonumber
\eeqry
%
where $\alpha, \beta ~\&~ \gamma$ are the Euler angles relating the two directions $\hat{n}_i$ and $\hat{n}_j$. A specific case of this function with $(s=2, \ell_{\rm min}=2, \ell_{\rm max}=96)$ is depicted in the last two columns of \fig{fig:vis_kernel}.

>>>>

The spin spherical harmonic functions satisfy the following completeness relation,
%
\beq
\sum_{\ell m}{_sY_{\ell m}}(\hat{n}_i){_sY^*_{\ell m}}(\hat{n}_j) = \delta(\hat{n}_i - \hat{n}_j) \label{eq:ylmortho2} \,,
\eeq
%
Note that the numerical validity of \eq{eq:ylmortho2} is strictly true only when the sums over the indices $(\ell, m)$ run to infinity. This is never true in practice, since the measured data invariable are band limited owing to the finite resolution of the experiments. Hence this relation is only approximately true and in more realistic scenario takes up the following function form,
%
\beqry
\sum_{\ell=\ell_{\rm min}, m}^{\ell_{\rm max}}{_{s_1}Y^*_{\ell m}}(\hat{n}_i){_{s_2}Y_{\ell m}}(\hat{n}_j) &\approx& \delta(\hat{n}_i - \hat{n}_j) \label{eq:ylmortho2} \,, \\
&=& \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2 \ell+1}{4 \pi}} {}_{s_2}Y^{-s_1}_{\ell}(\beta,\alpha) e^{-i s_2 \gamma} \,, \nonumber
\eeqry
%
where $\alpha, \beta ~\&~ \gamma$ are the Euler angles relating the two directions $\hat{n}_i$ and $\hat{n}_j$. A specific case of this function with $(s=2, \ell_{\rm min}=2, \ell_{\rm max}=96)$ is depicted in the last two columns of \fig{fig:vis_kernel}.

### 2017-10-16 article/sections/kernel_discussion.tex
updates to the notebook evaluating the high res analysis, added latitude position of the mask as a input variable
added new figures to 353Ghz application ; minor edits to article
Updates to the real space derivation sections of the paper

\subsection{Visualizing the convolution kernels} \label{sec:visualize_operator}
We begin by evaluating the functions $f, _{+2}f ~\&~ _{-2}f $. Since these functions determine the amplitude of the convolution kernels as a function of the angular distance $\beta$ from the central pixel, we refer to them as the radial kernels. These functions have been calculated by evaluating the multipole sums in \eq{eq:rad_ker_queb} and \eq{eq:rad_ker_quequbqu} from $\ell_{\rm min}=2$ to $\ell_{\rm max}=96$. The resultant functions are depicted in \fig{fig:beta_kernel}. Note that the function $f(\beta)$, which is a part of the  real space convolution  kernel which translates the coordinate dependent Stokes Q \& U to coordinate independent scalars E \& B, has a vanishing contribution from the location of the central pixel ($\beta \rightarrow 0$). 
%
\begin{figure}[!hbt]
\centering
\includegraphics[width=0.8\columnwidth]{kernel/beta_kernel.pdf}
\caption{The figure depicts the radial part of the convolution kernels shown in \fig{fig:vis_kernel}. These radial function have been evaluated with the band limit fixed at $\ell_{\rm max}=96$. The vertical dashed line marks the approximate size of a NSIDE=32 Healpix pixel.}
\label{fig:beta_kernel}
\end{figure}
%
We recall that the fields E \& B are scalar and hence immune to coordinate definitions. The locally defined Stokes parameters however necessarily depend on the coordinate definition. Therefore, this nature of the radial kernel is to be expected in order for it to satisfy the requirement of the derived quantities being scalars. The functions $_{+2}f(\beta)~\&~_{-2}f(\beta)$, both contribute to the convolution kernels which decompose the Stokes parameters into those corresponding to the respective scalar modes E \& B. Note that while $_{-2}f(\beta)$ specifically contributes at the location of the central pixel, $_{+2}f(\beta)$ dominates in the neighbouring regions which are approximately at least 1 pixel away from the central pixel.

@@

>>>>

\subsection{Visualizing the convolution kernels} \label{sec:visualize_operator}
We begin by evaluating the functions $f, _{+2}f ~\&~ _{-2}f $. Since these functions determine the amplitude of the convolution kernels as a function of the angular distance $\beta$ from the central pixel, we refer to them as the radial kernels. These functions have been calculated by evaluating the multipole sums in \eq{eq:rad_ker_queb} and \eq{eq:f2_rad_ker} from $\ell_{\rm min}=2$ to $\ell_{\rm max}=96$. The resultant functions are depicted in \fig{fig:beta_kernel}. Note that the function $f(\beta)$, which is a part of the  real space convolution  kernel which translates the coordinate dependent Stokes Q \& U to coordinate independent scalars E \& B, has a vanishing contribution from the location of the central pixel ($\beta \rightarrow 0$). 
%
\begin{figure}[!hbt]
\centering
\includegraphics[width=0.8\columnwidth]{kernel/beta_kernel.pdf}
\caption{The figure depicts the radial part of the convolution kernels shown in \fig{fig:vis_kernel}. These radial function have been evaluated with the band limit fixed at $\ell_{\rm max}=96$. The vertical dashed line marks the approximate size of a NSIDE=32 Healpix pixel. \comment{Update to Nside=64 ?}}
\label{fig:beta_kernel}
\end{figure}
%
We recall that the fields E \& B are scalar and hence immune to coordinate definitions. The locally defined Stokes parameters however necessarily depend on the coordinate definition. Therefore, this nature of the radial kernel is to be expected in order for it to satisfy the requirement of the derived quantities being scalars. The functions $_{+2}f(\beta)~\&~_{-2}f(\beta)$, both contribute to the convolution kernels which decompose the Stokes parameters into those corresponding to the respective scalar modes E \& B. Note that while $_{-2}f(\beta)$ specifically contributes at the location of the central pixel, $_{+2}f(\beta)$ dominates in the neighbouring regions which are approximately at least 1 pixel away from the central pixel.

@@

%\captionsetup[subfigure]{labelformat=empty}
